Structuring College Access

### 2025-03-13 index.qmd
update maps + add qr code

      # Add RQ1 map
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines("#### Map")

@@

      writeLines(str_c('<iframe data-src="', rq1_map, '" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))
      writeLines('<p class="fullscreen">Fullscreen</p>')

@@

      # Add RQ2 map
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines("#### Map")

      writeLines(str_c(
        '<iframe data-src="./results/maps/rq2_map_',
        m,
        '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'
      ))
      writeLines('<p class="fullscreen">Fullscreen</p>')

@@

    # Build figure name and call your "no-heading" figure function
    graph_type <- paste0(g, "_", rc, "_plot_", native_order)
    insert_figure_aian(
      rq         = "rq2",
      metro      = m,
      graph_type = graph_type
    )
  }
}
```

@@

>>>>

      # Add RQ1 map
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines(str_c("#### Racial/ethnic and socioeconomic characteristics of ", heading_text, " Geomarkets over time"))

@@

      writeLines(str_c('<iframe data-src="', rq1_map, '" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))
      writeLines('<p class="fullscreen">Fullscreen</p>')
      writeLines('<div class="footnote">Figure Notes:<br>- Race/ethnicity categories not available in 1980 Census: Asian, non-Hispanic; Two+ races, non-Hispanic; NHPI, non-Hispanic; AIAN non-Hispanic<br>- Household income measured using 2024 CPI</div>')

@@

      # Add RQ2 map
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines(str_c("#### Purchased student profiles by racial/ethnic composition and first-generation status, ", heading_text))

      writeLines(str_c(
        '<iframe data-src="./results/maps/rq2_map_',
        m,
        '.html" src="about:blank" width=100% height=100% style="max-height: 75%" allowtransparency="true"></iframe>'
      ))
      writeLines('<p class="fullscreen">Fullscreen</p>')
      notes_txt <- readLines(file.path(graphs_dir, rq, str_c('rq2_', m, '_race_row_plot_note.txt')), warn = FALSE)
      writeLines(
        str_replace(
          str_c('<div class="footnote">', paste0(notes_txt, collapse = "</br>"), '</div>'),
          'Excludes students with missing values for race\\. ', ''
        )
      )

@@

    # Build figure name and call your "no-heading" figure function
    graph_type <- paste0(g, "_", rc, "_plot_", native_order)
    insert_figure_aian(
      rq         = "rq2",
      metro      = m,
      graph_type = graph_type
    )
  }

  # Add RQ2 map
  writeLines(paste0("### ", heading_text, " (AI/AN) {.hide}\n"))
  writeLines(str_c("#### Purchased AI/AN student profiles by racial/ethnic composition and first-generation status"))

  writeLines(str_c(
    '<iframe data-src="./results/maps/rq2_aian_map_',
    m,
    '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'
  ))
  writeLines('<p class="fullscreen">Fullscreen</p>')
  writeLines('<div class="footnote">Figure Notes:<br>- Order number 487927 (ordered 7/19/2019): HS class 2020 OR 2021; Ethnicity/Race = American Indian or Alaska Native; SAT 1040-1600; GPA B- to A+.</div>')
}
```

@@

# Thank you!{.align-center}

<div><img class="qr" src="./assets/images/qr_code.png" /></div>
